---
title: "Fun Puzzles Study 1 Modeling"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
    #code_folding: "hide"
    df_print: paged
---

## Set up
```{r}
rm(list=ls())
```

```{r setup, include=FALSE, warning=F, message=F}
if(!require("pacman")) install.packages("pacman")
pacman::p_load('tidyverse','here','broom','lme4')

here::i_am("analysis/study1/corpus_analysis.Rmd")

set.seed(12341)

```

## Import data

```{r}
# puzzles metadata
sokobanonline_data = read_csv(here('data','study1', 'full_sokobanonline_df.csv')) |>
  select(-`...1`)
```

## 1) Summary Stats

#### A) dataset: authors, collections, puzzles
```{r}
print(paste0("num authors: ",length(unique(sokobanonline_data$Author_Name)))) 
print(paste0("num collections: ", length(unique(sokobanonline_data$Collection_Name)))) 
print(paste0("num puzzles: ",length(unique(sokobanonline_data$id)))) 
print(paste0("num reactions: ",sum(sokobanonline_data$num_reactions)))
print(paste0("num likes: ",sum(sokobanonline_data$likes)))
```

#### B) puzzle features

- prop_floor = "openess"
- num_valid_tiles = "puzzle area"
- tedium = "steps per box"
- astar_iters = "search complexity"

```{r}
visual_features_columns = c('num_boxes', 'num_valid_tiles', 'propFloor' )
solution_columns = c('completion_rate', 'optimal_solution_length', 'astar_iters', 'tedium')
enjoyment_columns = c('like_rate', 'like_ratio')

# Calculate summary statistics for all or selected columns
summary_stats <- sokobanonline_data |> 
  pivot_longer(
    cols = c(visual_features_columns, solution_columns, enjoyment_columns),
    names_to = "Variable",
    values_to = "Value"
  ) |>
  group_by(Variable) |> 
  summarise(
    mean = mean(Value, na.rm = TRUE),
    median = median(Value, na.rm = TRUE),
    sd = sd(Value, na.rm = TRUE),
    min = min(Value, na.rm = TRUE),
    max = max(Value, na.rm = TRUE)
  )

# View results
print(summary_stats)

```

## 2) Correlations with Like Rate

### A) cook's distance (high leverage points)

```{r}
model <- lm(like_rate ~ propFloor, data = sokobanonline_data)
cooksD <- cooks.distance(model)
influential <- cooksD[(cooksD > (3 * mean(cooksD, na.rm = TRUE)))]
names_of_influential <- names(influential)
```


### B) correlations (removing high leverage points)

```{r}
pearson_noinfluence <- function(df, variable) {
  # Construct formula dynamically
  formula <- reformulate(variable, response = "like_rate")
  # Fit the first model
  model1 <- lm(formula, data = df)
  # Calculate Cook's Distance
  cooksD <- cooks.distance(model1)
  # Identify influential points
  threshold <- 3 * mean(cooksD, na.rm = TRUE)
  influential <- which(cooksD > threshold)  # Get row indices
  # Subset data excluding influential points
  df2 <- df[-influential, , drop = FALSE]  # Drop influential rows safely
  # Fit the second model on filtered data
  model2 <- lm(formula, data = df2)
  
  pearson_corr = cor.test(df2$like_rate, df2[[variable]])
  
  return(tibble(r = sqrt(summary(model2)$r.squared),
              varname = variable,
              tidy(pearson_corr)#$estimate[[1]]
              #r.p = summary(model2)$coefficients[, 4][[2]]
              ))
  }


results_df <- tibble(vars= c("num_valid_tiles", "propFloor", "num_boxes", "tedium", "astar_iters")) |>
  mutate(result = lapply(vars, function(var) pearson_noinfluence(sokobanonline_data, variable = var))) |>
  unnest() |>
  select(-varname, - alternative)

print(results_df)

```

### C) correlation bar plot (fig 3A)

```{r}
var_order <- c("astar_iters","tedium", "num_boxes", "propFloor","num_valid_tiles")

results_df <- results_df |> mutate(
  star_x = ifelse(estimate >= 0, estimate + 0.02, estimate - 0.02)
)


bar_pearson_like = ggplot(results_df |>  mutate(vars = factor(vars, levels = var_order)),
                          aes(x = estimate,
                          y = vars)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_text(
    # Add stars for significant p-values
    data = results_df |> filter(p.value < 0.05) |> mutate(vars = factor(vars, levels = var_order)),
    aes(label = "*", x = star_x),  
    vjust = 0.8, hjust = 0, size = 10) +
  scale_x_continuous(
    limits = c(-0.35, 0.35),  # Keep same x-axis limits
    breaks = seq(-0.4, 0.4, by = 0.1)  
  ) +
  theme_minimal() +
  theme(panel.grid.minor.x = element_blank(),
        axis.line = element_line(color = "black", linewidth = .5))

bar_pearson_like
```

## 3) Modeling with Like Rate 

### A) like rate ~ completion rate & (completion rate)^2

```{r}
likeRate_model = lm(
  like_rate ~ 1,
  data = sokobanonline_data
)

likeRate_Completion_model = lm(
  like_rate ~ 1 + 
    completion_rate,
  data = sokobanonline_data
)

anova(likeRate_model, likeRate_Completion_model)

likeRate_CompletionSq_model <- lm(
  like_rate ~ 1 +
    completion_rate +
    I(completion_rate^2), 
  data = sokobanonline_data
)

anova(likeRate_Completion_model, likeRate_CompletionSq_model)
```

### B) like rate ~ other features 

```{r}
likeRate_visualFeatures_model <- lm(
  like_rate ~ 1 +
    propFloor + 
    num_valid_tiles +
    num_boxes, 
  data = sokobanonline_data
)

anova(likeRate_model, likeRate_visualFeatures_model)
print(paste0('adjusted R^2:', summary(likeRate_visualFeatures_model)$adj.r.squared))

likeRate_AllFeatures_model <- lm(
  like_rate ~ 1 +
    propFloor + 
    num_valid_tiles +
    num_boxes +
    completion_rate + 
    optimal_solution_length +
    astar_iters + 
    tedium, 
  data = sokobanonline_data
)

anova(likeRate_model, likeRate_AllFeatures_model)
print(paste0('adjusted R^2:', summary(likeRate_AllFeatures_model)$adj.r.squared))
```

### C) plotting marginal histogram (fig 3B)

```{r}
jc_theme = theme(base_size=20,
  plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
  plot.background = element_rect(fill = "white", color = NA),
  plot.title = element_text(
    size = 11, face = "bold",
    hjust = 0.5,
    margin = margin(b = 15)
  ),
  axis.line = element_line(color = "black", linewidth = .5),
  axis.title = element_text(
    size = 14, color = "black",
    face = "bold",
    # family="Avenir"
  ),
  axis.text = element_text(size = 9, color = "black"),
  axis.text.x = element_text(margin = margin(t = 5)),
  axis.title.y = element_text(margin = margin(r = 5)),
  axis.ticks = element_line(size = .5)#,
  )
```

```{r, fig.height = 3, fig.width = 3}
line_color = "orange"
histogram_plot = ggplot(sokobanonline_data, aes(x = completion_rate, 
                                                            y = like_rate,
                                                            color = num_boxes
                                                              )) + 
  geom_point(alpha = 1, shape = 16, size = 1.25) +
  scale_color_gradient(low = "grey80", high = "black", breaks = seq(1, 11, by = 1)) + 
  geom_smooth(method = "lm", formula = y ~ x + I(x^2), color = line_color, se= TRUE,fill = line_color, alpha = 0.2) +
  scale_y_continuous(labels = scales::percent) +  scale_x_continuous(labels = scales::percent) +
  labs(
    title = "",
    x = 'Completion Rate',
    y = 'Like Rate'#,
  ) +
  jc_theme +
  theme(
    legend.position = c(0.05, 0.95),  
    legend.justification = c(0, 1),  
    legend.direction = "horizontal",  
    legend.text = element_text(size = 6), 
    legend.key.size = unit(0.5, "lines"),  
    legend.spacing.x = unit(0.2, "lines"), 
    legend.margin = margin(t = -5, r = -5, b = -5, l = -5) 
  )

marginal_histogram = ggExtra::ggMarginal(histogram_plot, type = "histogram")

marginal_histogram

```